\clearpage\cftpagenumbersoff{chapter}
\chapter{List of Publications}
\thispagestyle{empty}
\pagestyle{empty}

\textbf{Published}
\begin{enumerate}
\item J.S. Teh and A. Samsudin. A stream cipher based on spatiotemporal chaos and true random synchronization. IETE Journal of Research, 2017. \newline DOI: 10.1080/03772063.2017.1284617 \newline [Scopus, ISI] [ISI IF: 0.284]
\item J.S. Teh and A. Samsudin. A chaos-based authenticated cipher with associated data. Security and Communication Networks, 2017. DOI: 10.1155/2017/9040518 \newline [Scopus, ISI] [ISI IF: 0.806]
\item J.S. Teh, W. Teng and A. Samsudin. A true random number generator based on hyperchaos and digital sound. in International Conference on Computer \& Information Sciences (ICCOINS 2016), Kuala Lumpur, Malaysia: IEEE Xplore. DOI: 10.1109/ICCOINS.2016.7783225 \newline [Scopus]
\item J. Chen, J.S. Teh, C. Su, A. Samsudin and J. Fang. Improved (related-key) attacks on round-reduced KATAN-32/48/64 based on the extended boomerang framework. In K.J. Liu \& R. Steinfeld (Eds.), Information Security and Privacy: 21st Australasian Conference, ACISP 2016 (pp. 333-346). Melbourne, Australia: Springer International Publishing. DOI: 10.1007/978-3-319-40367-0\_21 \newline [Scopus, ISI]
\item J.S. Teh, A. Samsudin, M. Al-Mazrooie and A. Akhavan. GPUs and chaos: a new true random number generator. Nonlinear Dynamics. 82(4), pp. 1913-1922, 2015. DOI: 10.1007/s11071-015-2287-7 \newline [Scopus, ISI] [ISI IF: 3.000]
\end{enumerate}

\textbf{In Press}
\begin{enumerate}[resume]
\item J. Chen, J.S. Teh, C. Su, A. Samsudin and Y. Xiang. Data Confidentiality: A Searching Strategy for Accurate Statistical Analysis of Security Margins. IEEE Transactions on Computers. \newline [Scopus, ISI] [ISI IF: 1.723]
\item J.S. Teh, W. Teng and A. Samsudin. Hyperchaos and Digital Sound: A New True Random Number Generator with Security Evaluation. Jurnal Teknologi. \newline [Scopus]
\end{enumerate}
\newpage
\textbf{Other Published Work}
\begin{enumerate}[resume]
\item J.S. Teh, A. Samsudin and A. Akhavan. Parallel chaotic hash function based on the shuffle-exchange network. Nonlinear Dynamics. 81(3), pp. 1067-1079, 2015. DOI: 10.1007/s11071-015-2049-6 \newline [Scopus, ISI] [ISI IF: 3.000]
\end{enumerate}

\textbf{Under Review}
\begin{enumerate}[resume]
\item J.S. Teh, A. Akhavan and A. Samsudin. Harvesting noise from multi-core CPUs: a new true random number generator with security evaluation. Submitted to Fluctuation and Noise Letters. \newline [1st Revision] [Scopus, ISI]
\end{enumerate}

\clearpage\pagestyle{plain}